Quasi-consistent efficient meshfree thin shell formulation with penalty-free essential boundary condition enforcement

### 2024-03-22 response.tex

\textbf{3.} $\boldsymbol \theta$ \textit{is the variation of $\boldsymbol a_3$, so $\boldsymbol \theta \cdot \boldsymbol a_3=0$. This relationship does not come from $\epsilon_{3i} = 0$, which was in Eq. (9).}

\textbf{Reply:} Thanks, the reviewer is right, the rotation $\boldsymbol \theta$ is perpendicular to $\boldsymbol a_3$. However, this relationship is also equivalent with $\epsilon_{3i}=0$, which follows the Kirchhofff hypothesis and can be easily evidenced by expression of Eq. (9).

\textbf{4.} \textit{Eq. (10) seems to be wrong. Where is $\boldsymbol a_{3,\alpha}$ and where is the most complicated term $\boldsymbol \theta_{,\alpha}$?}

\textbf{Reply:} Thank you for this comment. The detailed dervation of Eq. (10) is given by the following steps:
\begin{equation}
    \begin{split}
        \kappa_{\alpha\beta} &=\frac{1}{2}(\boldsymbol a_{3,\alpha} \cdot \boldsymbol v_{,\beta} + \boldsymbol v_{,\alpha} \cdot \boldsymbol a_{3,\beta} + \boldsymbol a_\alpha \cdot \boldsymbol \theta_{,\beta} + \boldsymbol \theta_{,\alpha} \cdot \boldsymbol a_\beta) \\
        &=\frac{1}{2} \left ( 
        \begin{split}
            &\underbrace{(\boldsymbol a_3 \cdot \boldsymbol v_{,\beta})_{,\alpha} - \boldsymbol a_3 \cdot \boldsymbol v_{,\alpha\beta}}_{\boldsymbol a_{3,\alpha} \cdot \boldsymbol v_{,\beta}} \\
            +&\underbrace{(\boldsymbol a_3 \cdot \boldsymbol v_{,\alpha})_{,\beta} - \boldsymbol a_3 \cdot \boldsymbol v_{,\alpha\beta}}_{\boldsymbol v_{,\beta} \cdot \boldsymbol a_{3,\alpha}} \\
            -& \boldsymbol a_\alpha \cdot \underbrace{((\boldsymbol v_{,\gamma} \cdot \boldsymbol a_3)_{,\beta} \boldsymbol a^\gamma + \boldsymbol v_{,\gamma} \cdot \boldsymbol a_3 \boldsymbol a^\gamma_{,\beta})}_{-\boldsymbol \theta_{,\beta}} \\
            -& \boldsymbol a_\beta \cdot \underbrace{((\boldsymbol v_{,\gamma} \cdot \boldsymbol a_3)_{,\alpha} \boldsymbol a^\gamma + \boldsymbol v_{,\gamma} \cdot \boldsymbol a_3 \boldsymbol a^\gamma_{,\alpha})}_{-\boldsymbol \theta_{,\alpha}} \\
        \end{split}
        \right ) \\
        &=\frac{1}{2} \left ( 
        \begin{split}
            &\underbrace{(\boldsymbol a_3 \cdot \boldsymbol v_{,\beta})_{,\alpha}
            +(\boldsymbol a_3 \cdot \boldsymbol v_{,\alpha})_{,\beta}
            -(\boldsymbol v_{,\alpha} \cdot \boldsymbol a_3)_{,\beta}
            -(\boldsymbol v_{,\beta} \cdot \boldsymbol a_3)_{,\alpha}}_{0} \\
            -&2\boldsymbol a_3 \cdot \boldsymbol v_{,\alpha\beta}
            - \boldsymbol v_{,\gamma} \cdot \boldsymbol a_3 \underbrace{\boldsymbol a_\alpha \cdot \boldsymbol a^\gamma_{,\beta}}_{-\Gamma_{\alpha\beta}^\gamma}
            - \boldsymbol v_{,\gamma} \cdot \boldsymbol a_3 \underbrace{\boldsymbol a_\beta \cdot \boldsymbol a^\gamma_{,\alpha}}_{-\Gamma_{\alpha\beta}^\gamma} \\
        \end{split}
        \right ) \\
        &= (\Gamma_{\alpha\beta}^\gamma \boldsymbol v_{,\gamma} - \boldsymbol v_{,\alpha\beta}) \cdot \boldsymbol a_3
    \end{split}
\end{equation}
The detailed derivation can be found in reference (Benzaken et al. 2021). For the conciseness, the detailed derivation of Eq. (10) is not listed in manuscript, and the related statement has been added on Page 6.

@@

\textbf{5.} \textit{Patchtest: table 2 is interesting. Eq. (62) assumes the solution is only polynomials on the mid-surface, which is already not a polynomial in the Cartesian coordinate. The flat model is simple, in this case, the parametric domain is the same as Cartesian. I believe the error in the curved case is due to bad parametrization. In general, the solution should be able to reproduce the parametric polynomials if the integration and parametrization are both good.}

\textbf{Reply:} Thank you for your comment. As we can find in Eqs. (32), (33), (35), (36),  the proposed approach was designated for polynomial strains and stresses. For flat model, the polynomial displacement leads to the polynomial strains and stresses. However, for curved model, the only polynomial strains can be got, the stresses turn to be non-polynomial due to the parametrization of curvilinear coordinates. As a result, even the integration and parametrization are well posed, the approximated smoothed stresses cannot exactly reproduce this non-polynomial stresses. That is why the approach was named with "quasi-consistent".

@@

\textbf{6.} \textit{Example 5.2, figure (7) is distracting. The purpose of the newly designed method is to get rid of the penalty parameters. In general, the final penalty parameter should be $E/h\times C$, where $C$ is a dimensionless coefficient. If one is testing the convergence rate of Nitsche or penalty methods, the penalty parameter needs to be scaled by the mesh size $h$, when the model is refined.}

\textbf{Reply:} Following the reviewer's suggestion, the artificial parameters using in Figure (7) are scaled by support size of shape function $s$ that can represent the grid size of discrete model $h$. In accordance with reference [4], the parameters were set as $\alpha_{v\alpha} = \bar\alpha_v / s$, $\alpha_{v3} = \bar\alpha_v / s^3$ and $\alpha_\theta = \bar \theta / s$, in which $\alpha_{v\alpha}$'s and $\alpha_{v3}$ have been redefined as the parameters referring to in-plane displacements $\boldsymbol v \cdot \boldsymbol a_\alpha$ and deflection $\boldsymbol v \cdot \boldsymbol a_3$ respectively. After these parameters scaling by support size, Nitsche's method and penalty method shows less parameter sensitivity, but cannot totally eliminate this. The related statements are added on Pages 17, 18 and 21.

@@

\textbf{7.} \textit{In Example 5.2, the authors provided the wrong reference value. $-0.3024$ is the one under RM shell theory. In this case, I believe the value should be $-0.3006$. See [1] for more information.}

\textbf{Reply:} Thank you for your suggestion, the reference value has been changed to $-0.3006$. Accordingly, the related statement on Page 21 has been modified.

@@

\textbf{8.} \textit{In Example 6.2, also check if the reference value provided in this study is for RM shells [2].}

\textbf{Reply:} Following the reviewer's suggestion, the reference value has been updated in Fig. 10 on Page 26. For showing a better convergence performance, the meshfree discretizations were changed to that ranging from $16\times16$ to $40\times40$. The relate description also has been revised on Page 21.

@@

\textbf{3.} \textit{Please provide the meaning of the symbol $s_{\alpha I}$ in Eq. (25). What is the parameter value used in this paper?}

\textbf{Reply:} Thanks for this comment. $s_{\alpha I}$ means the support size of the shape function $\Psi_I$. Following the suggestion, this related statement has been added on Page 9 and the authors have also doubly checked that all the symbols in manuscript have been properly defined.

\textbf{4.} \textit{Fig. 2 contains two sets of integration points. Considering the computational burden, using only one set of integration points may be more beneficial for Galerkin meshfree methods. Therefore, it is recommended to provide some explanations.}

\textbf{Reply:} Thanks for this comment. These two integration scheme contribute different procedures. For instance, in the procedures with blue integration points, there exist both domain integration and boundary integration in each integration cells. The total number of these blue integration points has been optimized from a global point of view to reduce the computation of meshfree shape functions and their first order derivatives. The detailed discussion of these optimized integration scheme can be found in [5].

@@

On the other hand, the red cross integration points are employed for assembly of stiffness matrix that does not involve any boundary integration, only the integration accuracy is considered for choosing a proper scheme. Thus, the traditional 3-point integration scheme is sufficient for this task. If this integration scheme uses the identical points with blue ones, the number of integration points for assembly have to be two-fold increased, which will lower the efficiency.

Consequently, so far, the integration schemes are the best choice for the proposed method. The related discussion has been added on Page 16.

\textbf{5.} \textit{On page 13, the authors stated that "Even with p-th order variational consistency, the proposed formulation can not exactly reproduce the solution spanned by basis functions". The reproducibility is important for Galerkin meshfree methods. So, just suggestion, is it possible to give some more explicit explanations.}

\textbf{Reply:} Thanks a lot for this helpful comment. This reproducibility is a requirement for the variational consistency, and it is the necessary to achieve the optimal accuracy for Galerkin formulations. The related discussions about the reproducibility and consistency condition have been added on Page 2.

@@

\textbf{Reply:} Following the reviewer's suggestion, the artificial parameters used in NItsche's method and penalty method have been added on Page 19. And the additional demonstrations for RKGSI-penalty also have been added on Pages 19 and 20.

\textbf{7.} \textit{On pages 32-34, some reference information such as journal title and year of publication is missed.}

\textbf{Reply:} Thanks a lot, following the reviewer's suggestion, these reference's information have been revised, the authors also have doubly checked all the information and formats of references.

\section*{References}
\begin{enumerate}[{[1]}]
    \item P. Krysl, J.S. Chen, Benchmarking computational shell models, Archives of Computational Methods in Engineering 30 (2023) 301–315. 
    \item J. Kiendl, K.U. Bletzinger, J. Linhard, R. Wüchner, Isogeometric shell analysis with Kirchhoff–Love elements, Computer Methods in Applied Mechanics and Engineering 198 (2009) 3902–3914. 
    \item T. Belytschko, H. Stolarski, W.K. Liu, Stress projection for membrane and shear locking in shell finite elements, Computer Methods in Applied Mechanics and Engineering 51 (1985) 221–258. 
    \item J. Benzaken, J.A. Evans, S.F. McCormick, R. Tamstorf, Nitsche’s method for linear Kirchhoff–Love shells: Formulation, error analysis, and verification, Computer Methods in Applied Mechanics and Engineering 374 (2021) 113544. 
    \item D. Wang, J. Wu, An inherently consistent reproducing kernel gradient smoothing framework toward efficient Galerkin meshfree formulation with explicit quadrature, Computer Methods in Applied Mechanics and Engineering 349 (2019) 628–672. 
\end{enumerate}
\end{document}

### 2024-03-22 boundary.tex
20240322

With the approximated effective stresses and strains, the last equation of weak form becomes:

@@

the left side of Eq. (\ref{w51}) can be simplified by following steps. For clarity, the derivation of first term in Eq. (\ref{w51}) regarding as an example is given by:

@@

and further substituting Eqs. (\ref{epsilon2}), (\ref{kappa2}) into above equation gives the final discrete equilibrium equations: 

@@

The detailed derivations of Eqs (\ref{de1})-(\ref{de3}) are listed in the Appendix \ref{derivations}. As shown in these equations, the Eq. (\ref{de1}) is the conventional stiffness matrix evaluated by smoothed gradients $\tilde \Psi_{I,\alpha}$, $\tilde \Psi_{I,\alpha}\vert_\beta$, and the Eqs. (\ref{de2}) and (\ref{de3}) contribute for the enforcement of essential boundary. It should be mentioned that, in accordance with reproducing kernel smoothed gradient framework, the integration scheme of Eqs. (\ref{de1}-\ref{de3}) should be aligned with the those used in the construction of smoothed gradients. With a close look with Eqs. (\ref{de2}) and (\ref{de3}), the proposed approach for enforcing essential boundary conditions show an identical structure with traditional Nitsche's method, both have the consistent term and stabilized term. So the next subsection will review the Nitsche's method and compare it with proposed method.

@@

The Nitsche's method for enforcing essential boundary can be regarded as a combination of Lagrangian multiplier method and penalty method, in which the Lagrangian multiplier is represented by the approximated displacement. The corresponding total potential energy functional $\Pi_P$ is given by:

@@

                     &+ \underbrace{\frac{\alpha_v}{2} \int_{\Gamma_v} \boldsymbol v \cdot \boldsymbol v d\Gamma 

@@

             + \frac{\alpha_C}{2}(\boldsymbol v \cdot \boldsymbol v)_{\boldsymbol x\in C_v}}_{\text{stabilized term}}

@@

where the consistent term rephrased from Lagrangian multiplier method contributes to enforce the essential boundary and meet the variational consistency condition. However the consistent term can not always ensure the coercivity of stiffness, so the penalty method is introduced to be regarded as a stabilized term. With a standard variational argument, the corresponding weak form can be stated as:

@@

                     &+ \alpha_v \int_{\Gamma_v} \delta \boldsymbol v \cdot \boldsymbol v d\Gamma 

@@

                     + \alpha_C(\delta \boldsymbol v \cdot \boldsymbol v)_{\boldsymbol x\in C_v} \\

@@

in which $\alpha_v$, $\alpha_\theta$ and $\alpha_C$ are experimental artificial parameters. Further invoking the conventional reproducing kernel approximation of Eq. (\ref{approxv}) leads to the following discrete equilibrium equations:

@@

where the stiffness $\boldsymbol K_{IJ}$ is identical with Eq. (\ref{de1}). $\boldsymbol K^c_{IJ}$ and $\boldsymbol K^s_{IJ}$ are the stiffness matrix for consistent and stabilized terms respectively, and have the following forms:

@@

\boldsymbol K^s_{IJ} &= \alpha_v \int_{\Gamma_v} \Psi_I \Psi_J \boldsymbol 1 d\Gamma 

@@

\boldsymbol f^s_I &= \alpha_v \int_{\Gamma_v} \Psi_I \bar{\boldsymbol v} d\Gamma + \alpha_\theta \int_{\Gamma_\theta} \Psi_{I,\eta} n^\eta \boldsymbol a_3 \boldsymbol \bar \theta_{\boldsymbol n} d\Gamma + \alpha_C [[\Psi_I \boldsymbol a_3 \boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}

@@

Comparing with the consistent terms of Eqs (\ref{de2}) and (\ref{nde2}), their expression is almost identical, the major difference is that the higher order derivatives of shape functions have been replaced by smoothed gradients. Owing to the reproducing kernel framework, the construction of smoothed gradients only concerns about the computation of traditional meshfree shape functions and their first order derivatives, which avoids the costly computation of higher order derivatives. Moreover, the stabilized terms in Eq. (\ref{nd3}) employs the penalty method to ensure the coercivity of stiffness, in contrast, the stabilized term of Eq. (\ref{de3}) naturally exist in weak form, and it can stabilize the result without any artificial parameters.

>>>>

With the approximated effective stresses and strains, the last equation of weak form Eq. (\ref{w5}) becomes:

@@

The left side of Eq. (\ref{w51}) can be simplified using the following steps. For clarity, the derivation of first term in Eq. (\ref{w51}) taken as an example is given by:

@@

on further substituting Eqs. (\ref{epsilon2}) and (\ref{kappa2}) into above equation gives the final discrete equilibrium equations, respectively: 

@@

The detailed derivations of Eqs (\ref{de1})-(\ref{de3}) are listed in the \ref{derivations}. As shown in these equations, Eq. (\ref{de1}) is the conventional stiffness matrix evaluated by smoothed gradients $\tilde \Psi_{I,\alpha}$, $\tilde \Psi_{I,\alpha}\vert_\beta$, and the Eqs. (\ref{de2}) and (\ref{de3}) contribute for the enforcement of essential boundary. It should be mentioned that, in accordance with reproducing kernel smoothed gradient framework, the integration scheme of Eqs. (\ref{de1}-\ref{de3}) should be aligned with the those used in the construction of smoothed gradients. The integration scheme used for proposed method is shown in Fig. \ref{fig2}, in which the total number of the blue circular integration points has been optimized from a global point of view, aiming to reduce the computation of traditional meshfree shape functions and its first order derivatives. In contrast, for assembly stiffness matrix $\boldsymbol K$, the low order Gauss integration rule is suitable to ensure the accuracy due to the inherently variational consistency in smoothed gradients. The detailed positions and weight of integration points and the efficiency demonstration of this optimized integration scheme can be found in \cite{wang2019a, du2022}  With a close look at Eqs. (\ref{de2}) and (\ref{de3}), the proposed approach for enforcing essential boundary conditions show an identical structure with traditional Nitsche's method, both have the consistent and stabilized terms. So, the next subsection will review the Nitsche's method and compare it with the proposed method.

@@

The Nitsche's method for enforcing essential boundaries can be regarded as a combination of Lagrangian multiplier method and penalty method, in which the Lagrangian multiplier is represented by the approximated displacement. The corresponding total potential energy functional $\Pi_P$ is given by:

@@

                     &+ \underbrace{\sum_{i=1}^3\frac{\alpha_{vi}}{2} \int_{\Gamma_v} \boldsymbol v \cdot \boldsymbol v d\Gamma 

@@

             + \frac{\alpha_C}{2}(\boldsymbol v \cdot \boldsymbol a_3)^2_{\boldsymbol x\in C_v}}_{\text{stabilized term}}

@@

where the consistent term generated from the Lagrangian multiplier method contributes to enforce the essential boundary, and meet the variational consistency condition. However, the consistent term can not always ensure the coercivity of stiffness, so the penalty method is introduced to serve as a stabilized term, in which $\alpha_{vi}$'s, $\alpha_\theta$ and $\alpha_C$ are experimental artificial parameters in penalty method. With a standard variational argument, the corresponding weak form can be stated as:

@@

                     &+ \sum_{i=1}^{3}\alpha_{vi} \int_{\Gamma_v} (\delta \boldsymbol v \cdot \boldsymbol a_i) (\boldsymbol a_i \cdot \boldsymbol v) d\Gamma 

@@

                     + \alpha_C(\delta \boldsymbol v \cdot \boldsymbol a_3 \; \boldsymbol a_3 \cdot \boldsymbol v)_{\boldsymbol x\in C_v} \\

@@

Further invoking the conventional reproducing kernel approximation of Eq. (\ref{approxv}) leads to the following discrete equilibrium equations:

@@

where the stiffness $\boldsymbol K_{IJ}$ is identical with Eq. (\ref{de1}). $\boldsymbol K^c_{IJ}$ and $\boldsymbol K^s_{IJ}$ are the stiffness matrices for consistent and stabilized terms, respectively, and have the following form:

@@

\boldsymbol K^s_{IJ} &= \boldsymbol \alpha_v \int_{\Gamma_v} \Psi_I \Psi_J d\Gamma 

@@

\boldsymbol f^s_I &= \boldsymbol \alpha_v \int_{\Gamma_v} \Psi_I \bar{\boldsymbol v} d\Gamma + \alpha_\theta \int_{\Gamma_\theta} \Psi_{I,\eta} n^\eta \boldsymbol a_3 \boldsymbol \bar \theta_{\boldsymbol n} d\Gamma + \alpha_C [[\Psi_I \boldsymbol a_3 \boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}

@@

with
\boldsymbol \alpha_v = \begin{bmatrix}
    \alpha_{v1} & 0 & 0 \\
    0 & \alpha_{v2} & 0 \\
    0 & 0 & \alpha_{v3} \\
\end{bmatrix}

On comparing with the consistent terms of Eqs. (\ref{de2}) and (\ref{nde2}), the expressions were almost identical, the major difference is that the higher order derivatives of shape functions have been replaced by smoothed gradients. Owing to the reproducing kernel framework, the construction of smoothed gradients only concerned about the computation of traditional meshfree shape functions and their first order derivatives, which avoid the costly computation of higher order derivatives. Moreover, the stabilized terms in Eq. (\ref{nde3}) employs the penalty method with big enough artificial parameters to ensure the coercivity of stiffness. And the optimal values of these artificial parameters are proportional to the grid size of discrete model that can be represented by support size in meshfree approximation, where the $\alpha_{v\alpha} \propto s^{-1}$, $\alpha_{v3} \propto s^{-3}$, $\alpha_\theta \propto s^{-1}$, $\alpha_C \propto s^{-2}$\cite{benzaken2021}, and $s = \min\{s_{\alpha I}\}$. In contrast, the stabilized term of Eq. (\ref{de3}) naturally exists in its weak form, and can stabilize the result without considering any artificial parameters.

### 2024-03-22 boundary_v0.tex
20240322

The detailed derivations of Eqs (\ref{de1})-(\ref{de3}) are listed in the \ref{derivations}. As shown in these equations, Eq. (\ref{de1}) is the conventional stiffness matrix evaluated by smoothed gradients $\tilde \Psi_{I,\alpha}$, $\tilde \Psi_{I,\alpha}\vert_\beta$, and the Eqs. (\ref{de2}) and (\ref{de3}) contribute for the enforcement of essential boundary. It should be mentioned that, in accordance with reproducing kernel smoothed gradient framework, the integration scheme of Eqs. (\ref{de1}-\ref{de3}) should be aligned with the those used in the construction of smoothed gradients. The integration scheme used for proposed method is shown in Fig. \ref{fig2}, in which the total number of the blue circular integration points has been optimized from a global point of view, aiming to reduce the computation of traditional meshfree shape functions and its first order derivatives. In contrast, for assembly stiffness matrix $\boldsymbol K$, the low order Gauss integration rule is suitable to ensure the accuracy due to the inherently variational consistency in smoothed gradients. The detailed positions and weight of integration points and the efficiency demonstration of this optimized integration scheme can be found in \cite{wang2019a, du2022}  With a close look at Eqs. (\ref{de2}) and (\ref{de3}), the proposed approach for enforcing essential boundary conditions show an identical structure with traditional Nitsche's method, both have the consistent and stabilized terms. So, the next subsection will review the Nitsche's method and compare it with the proposed method.

@@

                     &+ \underbrace{\sum_{i=1}^3\frac{\alpha_{vi}}{2} \int_{\Gamma_v} \boldsymbol v \cdot \boldsymbol v d\Gamma 

@@

             + \frac{\alpha_C}{2}(\boldsymbol v \cdot \boldsymbol a_3)^2_{\boldsymbol x\in C_v}}_{\text{stabilized term}}

@@

where the consistent term generated from the Lagrangian multiplier method contributes to enforce the essential boundary, and meet the variational consistency condition. However, the consistent term can not always ensure the coercivity of stiffness, so the penalty method is introduced to serve as a stabilized term, in which $\alpha_{vi}$'s, $\alpha_\theta$ and $\alpha_C$ are experimental artificial parameters in penalty method. With a standard variational argument, the corresponding weak form can be stated as:

@@

                     &+ \sum_{i=1}^{3}\alpha_{vi} \int_{\Gamma_v} (\delta \boldsymbol v \cdot \boldsymbol a_i) (\boldsymbol a_i \cdot \boldsymbol v) d\Gamma 

@@

                     + \alpha_C(\delta \boldsymbol v \cdot \boldsymbol a_3 \; \boldsymbol a_3 \cdot \boldsymbol v)_{\boldsymbol x\in C_v} \\

@@

Further invoking the conventional reproducing kernel approximation of Eq. (\ref{approxv}) leads to the following discrete equilibrium equations:

@@

\boldsymbol K^s_{IJ} &= \boldsymbol \alpha_v \int_{\Gamma_v} \Psi_I \Psi_J d\Gamma 

@@

\boldsymbol f^s_I &= \boldsymbol \alpha_v \int_{\Gamma_v} \Psi_I \bar{\boldsymbol v} d\Gamma + \alpha_\theta \int_{\Gamma_\theta} \Psi_{I,\eta} n^\eta \boldsymbol a_3 \boldsymbol \bar \theta_{\boldsymbol n} d\Gamma + \alpha_C [[\Psi_I \boldsymbol a_3 \boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}

@@

with
\boldsymbol \alpha_v = \begin{bmatrix}
    \alpha_{v1} & 0 & 0 \\
    0 & \alpha_{v2} & 0 \\
    0 & 0 & \alpha_{v3} \\
\end{bmatrix}

On comparing with the consistent terms of Eqs. (\ref{de2}) and (\ref{nde2}), the expressions were almost identical, the major difference is that the higher order derivatives of shape functions have been replaced by smoothed gradients. Owing to the reproducing kernel framework, the construction of smoothed gradients only concerned about the computation of traditional meshfree shape functions and their first order derivatives, which avoid the costly computation of higher order derivatives. Moreover, the stabilized terms in Eq. (\ref{nde3}) employs the penalty method with big enough artificial parameters to ensure the coercivity of stiffness. And the optimal values of these artificial parameters are proportional to the grid size of discrete model that can be represented by support size in meshfree approximation, where the $\alpha_{v\alpha} \propto s^{-1}$, $\alpha_{v3} \propto s^{-3}$, $\alpha_\theta \propto s^{-1}$, $\alpha_C \propto s^{-2}$\cite{benzaken2021}, and $s = \min\{s_{\alpha I}\}$. In contrast, the stabilized term of Eq. (\ref{de3}) naturally exists in its weak form, and can stabilize the result without considering any artificial parameters.

>>>>

The detailed derivations of Eqs (\ref{de1})-(\ref{de3}) are listed in the \ref{derivations}. As shown in these equations, Eq. (\ref{de1}) is the conventional stiffness matrix evaluated by smoothed gradients $\tilde \Psi_{I,\alpha}$, $\tilde \Psi_{I,\alpha}\vert_\beta$, and the Eqs. (\ref{de2}) and (\ref{de3}) contribute for the enforcement of essential boundary. It should be mentioned that, in accordance with reproducing kernel smoothed gradient framework, the integration scheme of Eqs. (\ref{de1}-\ref{de3}) should be aligned with the those used in the construction of smoothed gradients. The integration scheme used for proposed method is shown in Fig. \ref{fig2}, the detailed positions and weight of integration points can be found in \cite{du2022}  With a close look at Eqs. (\ref{de2}) and (\ref{de3}), the proposed approach for enforcing essential boundary conditions show an identical structure with traditional Nitsche's method, both have the consistent and stabilized terms. So, the next subsection will review the Nitsche's method and compare it with the proposed method.

@@

                     &+ \underbrace{\frac{\alpha_v}{2} \int_{\Gamma_v} \boldsymbol v \cdot \boldsymbol v d\Gamma 

@@

             + \frac{\alpha_C}{2}(\boldsymbol v \cdot \boldsymbol v)_{\boldsymbol x\in C_v}}_{\text{stabilized term}}

@@

where the consistent term generated from the Lagrangian multiplier method contributes to enforce the essential boundary, and meet the variational consistency condition. However, the consistent term can not always ensure the coercivity of stiffness, so the penalty method is introduced to serve as a stabilized term. With a standard variational argument, the corresponding weak form can be stated as:

@@

                     &+ \alpha_v \int_{\Gamma_v} \delta \boldsymbol v \cdot \boldsymbol v d\Gamma 

@@

                     + \alpha_C(\delta \boldsymbol v \cdot \boldsymbol v)_{\boldsymbol x\in C_v} \\

@@

in which $\alpha_v$, $\alpha_\theta$ and $\alpha_C$ represent experimental artificial parameters. Further invoking the conventional reproducing kernel approximation of Eq. (\ref{approxv}) leads to the following discrete equilibrium equations:

@@

\boldsymbol K^s_{IJ} &= \alpha_v \int_{\Gamma_v} \Psi_I \Psi_J \boldsymbol 1 d\Gamma 

@@

\boldsymbol f^s_I &= \alpha_v \int_{\Gamma_v} \Psi_I \bar{\boldsymbol v} d\Gamma + \alpha_\theta \int_{\Gamma_\theta} \Psi_{I,\eta} n^\eta \boldsymbol a_3 \boldsymbol \bar \theta_{\boldsymbol n} d\Gamma + \alpha_C [[\Psi_I \boldsymbol a_3 \boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}

@@

On comparing with the consistent terms of Eqs. (\ref{de2}) and (\ref{nde2}), the expressions were almost identical, the major difference is that the higher order derivatives of shape functions have been replaced by smoothed gradients. Owing to the reproducing kernel framework, the construction of smoothed gradients only concerned about the computation of traditional meshfree shape functions and their first order derivatives, which avoid the costly computation of higher order derivatives. Moreover, the stabilized terms in Eq. (\ref{nde3}) employs the penalty method to ensure the coercivity of stiffness. In contrast, the stabilized term of Eq. (\ref{de3}) naturally exists in its weak form, and can stabilize the result without considering any artificial parameters.
